Initial Analysis

### 2019-09-18 Initial_Analysis.Rmd
Creeated a function to fix the coding errors, not working fully. Will deal with it later

  # Cleaned results 
  Clean_Results <- Auto_Remove_Territories %>% 
    anti_join(Territories_to_Remove,
              by = c("Territory","Neighbour")
    ) %>% 
    filter(Same_Nation == "No") %>% 
    select(-8,-9)

@@

  # Load and clean Discrete results
  Non_Transboundary_Data <- fread(paste(Results_Path,"/Trans_Results/Non_Transboundary_Data.csv",sep="")) %>% 
    filter(!is.na(TaxonKey)) %>% 
    select(2:3)

@@

@@

Plot <- ggplot() +
  # geom_sf(data = World_sf_si_land,aes(fill = Bins), colour = "grey80") +
  geom_sf(data = World_sf_si,aes(fill = Bins),colour = "grey20") + # n_trans_spp or Bins
  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80") + # n_trans_spp or Bins
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
                               rev(wes_palette(n = 4, name = "Darjeeling2"))
                               ),
                     na.value = "white"
  ) +
  # scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#FF0000","#FF0000"),
                     # na.value = "white"
  # ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map()

>>>>

  # Cleaned results 
  Clean_Results <- Auto_Remove_Territories %>% 
    anti_join(Territories_to_Remove,
              by = c("Territory","Neighbour")
    ) %>% 
    filter(Same_Nation == "No") %>% 
    select(-8,-9) %>% 
    # Fixe coding issues between MAC and Windows
    mutate(
    Territory = gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",Territory),
    Territory = gsub("C<f4>te d'Ivoire","Côte d'Ivoire",Territory),
    Territory = gsub("R<e9>union (France)","Réunion",Territory),
    Neighbour = gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",Neighbour),
    Neighbour = gsub("C<f4>te d'Ivoire","Côte d'Ivoire",Neighbour),
    Neighbour = gsub(" R<e9>union (France)","Réunion",Neighbour)
    )

@@

  # Load and clean Discrete results
  Non_Transboundary_Data <- fread(paste(Results_Path,"/Non_Transboundary_Data.csv",sep="")) %>% 
    filter(!is.na(TaxonKey)) %>% 
    select(2:3)

@@

World_sf_si %>% 
  filter(Territory == "Côte d'Ivoire")

@@

Plot <- ggplot() +
  geom_sf(data = World_sf_si_land,aes(fill = Bins), colour = "grey80") +
  geom_sf(data = World_sf_si,aes(fill = Bins),colour = "grey20") + # n_trans_spp or Bins
  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80") + # n_trans_spp or Bins
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
  #                              rev(wes_palette(n = 4, name = "Darjeeling2"))
  #                              ),
  #                    na.value = "white"
  # ) +
  scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#FF0000","#FF0000"),
  na.value = "white"
  ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map()
